### 2022-03-09 ms/PrestigeBias.tex
update

\subsection{Using social influence to reverse harmful traditions \citep{harmful_traditions}}
Social influence could be a powerful tool to end traditions, harmful or advantageous. Harmful traditions can be child marriage, open defecation, and domestic violence, to name a few. 
\citet{harmful_traditions} suggest a mechanism called \textit{spillover}. By their definition, a spillover is when an intervention affect a large enough group in a target population, so that others not included in the intervention starts changing their behavior as well. In their research, they found that there are individuals who act as \textit{agents}, who are often looked upon, and therefore they are ideal targets for interventions. This is the same concept as our role-models, where a more prestigious individual will be copied more, therefore spreading his trait wider in the population. Their research support therefore in our assumption that there are social biases, conformist influence specifically. They also suggest a way to use this phenomena to change existing traditions in a population. It is very clear however, that just as it can be used to end harmful traditions, the same agents could be used for any negative way that comes to mind. 
\clearpage
\bibliography{refs}
\bibliographystyle{apalike}
\end{document}

>>>>

\subsection{Using social influence to reverse harmful traditions \citep{harmful_traditions}}
Social influence could be a powerful tool to end traditions, harmful or advantageous. Harmful traditions can be child marriage, open defecation, and domestic violence, to name a few. 
\citet{harmful_traditions} suggest a mechanism called \textit{spillover}. By their definition, a spillover is when an intervention affect a large enough group in a target population, so that others not included in the intervention starts changing their behavior as well. In their research, they found that there are individuals who act as \textit{agents}, who are often looked upon, and therefore they are ideal targets for interventions. This is the same concept as our role-models, where a more prestigious individual will be copied more, therefore spreading his trait wider in the population. Their research support therefore in our assumption that there are social biases, conformist influence specifically. They also suggest a way to use this phenomena to change existing traditions in a population. It is very clear however, that just as it can be used to end harmful traditions, the same agents could be used for any negative way that comes to mind.

\subsection{The evolution of prestige \citep{prestige_evolution}}
One cannot mention prestige and cultural transmission without the work of \citet{prestige_evolution}. They as well distinguish between prestige and dominance. The latter is is defined by acquiring social status by using aggression, intimidation and violence. They also mention dominance is more common than prestige in non humans. Their definition of prestige is somewhat synonymous with ours. Specifically prestige is composed both of estimation in the eyes of people (our indicator/success trait) and commanding position in people's minds, i.e number of copiers people think they have, which they define as \textit{influence} (similar to our definition for influence).
In their paper, they show that prestige evolved from natural selection, as an efficient process to extract reproductive benefit from the flow of socially transmitted information. Simply put, prestige is a natural step where social learning exists, due to saving costs of individual learning.
It could be interesting in the future to enhance our model with this idea, i.e observing the copier trait of \textit{evaluation}, rather than only observing the evolution of the indicator trait copied.
\citet{prestige_evolution} suggest that the most skilled role-models will, on average, end up with most copiers. This is consistent with our findings, and in a way our model is a mathematical equivalent to their suggested model.

\clearpage
\bibliography{refs}
\bibliographystyle{apalike}
\end{document}
